Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/intro.tex

Information flow control (IFC) is a promising technique for addressing these
problems, by tracking the flow of sensitive data through a system and
confining untrusted code so that it cannot exfiltrate data, except as
per a information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in the design of these
systems is ensuring they can be implemented efficiently: when the
semantics specify that information flow must be tracked at a
fine-grained level, e.g., per value in the system,  it can lead to
impractical runtime overheads even for ordinary operations.

>>>>

Information flow control (IFC) is a promising technique for addressing these
problems by tracking the flow of sensitive data through a system. Untrusted
code is confined so that it cannot exfiltrate data, except as
per an information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in the design of these
systems is ensuring they can be implemented efficiently: when the
semantics specify that information flow must be tracked at a
fine-grained level, e.g., per value in the system,  it can lead to
impractical runtime overheads even for ordinary operations.
